Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-26 manuscript.tex
abstract

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
Why do neurons communicate through spikes? By definition, a spike, or action potential, is an all-or-none event which occurs at asynchronous times. In other words, spikes on one side occur or not without further details and second can occur at any continuous time. This stands in stark contrast to the discretized timing classically used in digital processing at the base of modern-day neural networks. In the living world, neural systems almost systematically use this so-called event-based representation. A better understanding of this phenomenon remains a fundamental challenge in neurobiology in order to better interpret the masses of recorded data. It is also an emerging topic in computer science to allow the efficient exploitation of a new class of sensors and event-based computers, called neuromorphic, which could allow significant gains in computing time and energy consumption ---a major societal mission in the age of the digital economy and of global warming.
}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
Why do neurons communicate through spikes? By definition, a spike is an all-or-none event which occurs at continuous times. In other words, spikes are on one side binary, they occur or not without further details,  and second can occur at any asynchronous time, without a centralized clock. This stands in stark contrast to the discretized timing classically used in digital processing at the base of modern-day neural networks. In the living world, neural systems almost systematically use this so-called event-based representation. A better understanding of this phenomenon remains a fundamental challenge in neurobiology in order to better interpret the masses of recorded data. It is also an emerging topic in computer science to allow the efficient exploitation of a new class of sensors and event-based computers, called neuromorphic, which could allow significant gains in computing time and energy consumption ---a major societal mission in the age of the digital economy and of global warming. In this review paper, we provide evidence from biology and engineering that the precise timing of spikes plays a key role for our understanding of efficient neural networks.
}
